Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-07 paper/main.tex
Added Supercop discussion

>>>>

\section{Validity of \ac{SUPERCOP} results}
Although we believe the \ac{SUPERCOP} toolkit and results give good indication
of how fast the different candidate implementations are, we do have som
comments on it.

\paragraph{Implementations does not conform to \ac{NIST} specification} for
many of the candidates. By this we mean that there is no Update()-function
available for all implementation, and that \ac{SUPERCOP} only measures speed of
hashing full bytestrings. This is also a hasle for programmer who want to use
the implementations in \ac{SUPERCOP}

\paragraph{Incorrect implementations} are present in \ac{SUPERCOP}. By this we
mean implementations that does not verify the \ac{KAT}s.

\parapgraph{Results are only valid for one specific computer}. The results we
used from \ac{SUPERCOP} are only valid for our specific computer, although it
gives an indication of which speeds can be achieved on similar computers, i.e.
32-bit. However to get a complete picture of the performance of the different
candidates one must look at different computers and architectures. This picture
might be obtained from looking at the results from all computeres measured by
\ac{SUPERCOP}.
